\documentclass[12pt, a4paper]{article}

% ── Packages ──
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{amsmath, amssymb, amsthm, mathtools}
\usepackage{geometry}
\usepackage{hyperref}
\usepackage{enumitem}
\usepackage{booktabs}
\usepackage{array}
\usepackage{caption}
\usepackage{algorithm}
\usepackage{algpseudocode}

\geometry{margin=1in}
\hypersetup{colorlinks=true, linkcolor=blue, citecolor=blue, urlcolor=blue}

% ── Theorem environments ──
\newtheorem{theorem}{Theorem}[section]
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{proposition}[theorem]{Proposition}
\newtheorem{corollary}[theorem]{Corollary}
\newtheorem{claim}[theorem]{Claim}
\theoremstyle{definition}
\newtheorem{definition}[theorem]{Definition}
\newtheorem{remark}[theorem]{Remark}
\newtheorem{example}[theorem]{Example}

% ── Macros ──
\newcommand{\R}{\mathbb{R}}
\newcommand{\N}{\mathbb{N}}
\newcommand{\Z}{\mathbb{Z}}
\newcommand{\Linf}{L^\infty}
\newcommand{\supp}{\operatorname{supp}}
\newcommand{\tv}{\operatorname{tv}}
\newcommand{\rev}{\operatorname{rev}}
\newcommand{\conv}{\operatorname{conv}}

% ══════════════════════════════════════════════════════════════════════
\title{%
  A Rigorous Proof Framework for Lower Bounds on the\\
  Autoconvolution Constant $C_{1a}$\\[6pt]
  \large Via the Cloninger--Steinerberger Branch-and-Prune Algorithm
}
\author{Jai Bajaj}
\date{\today}

\begin{document}
\maketitle

\begin{abstract}
We present a self-contained proof that the autoconvolution constant
$C_{1a}$ --- the infimum of
$\|f * f\|_{L^\infty} / \bigl(\int f\bigr)^2$ over nonnegative
functions supported on $[-\tfrac14, \tfrac14]$ --- satisfies a lower
bound certifiable by exhaustive computation.  Our starting point is the
framework of Cloninger and Steinerberger (2017), which we extend with a
multiscale cascade and tighter pruning.  The paper is organized around
the natural sequence of reductions: from continuous functions to bin
averages (Section~\ref{sec:bin}), from the continuous simplex to a
finite lattice (Section~\ref{sec:disc}), and finally to an exhaustive
search made tractable by pruning
(Sections~\ref{sec:testvalue}--\ref{sec:cascade}).
Section~\ref{sec:correctness} addresses the invariants that keep the
computation honest.  Throughout, we emphasize intuition alongside formal
statements.
\end{abstract}

\tableofcontents
\newpage

% ======================================================================
\section{Introduction}\label{sec:intro}
% ======================================================================

\subsection{The Constant $C_{1a}$}

Consider the class of nonnegative, integrable functions supported on
the interval $[-\tfrac14, \tfrac14]$:
\[
  \mathcal{F} \;=\; \Bigl\{
    f : \R \to \R_{\ge 0}
    \;\Big|\;
    \supp(f) \subseteq \bigl[-\tfrac14, \tfrac14\bigr],\;
    \int f > 0
  \Bigr\}.
\]

The \emph{autoconvolution} of $f$ is
\[
  (f * f)(t) \;=\; \int_{-\infty}^{\infty} f(x)\, f(t - x)\, dx.
\]
Since $\supp(f) \subseteq [-\tfrac14, \tfrac14]$, the
autoconvolution is supported on $[-\tfrac12, \tfrac12]$ and is itself
nonnegative.

A natural question is: how small can the peak of $f * f$ be, relative
to the total mass of $f$?  This is precisely what $C_{1a}$ measures.

\begin{definition}
The \emph{autoconvolution constant} is
\[
  C_{1a} \;=\; \inf_{f \in \mathcal{F}} \;
  \frac{\displaystyle\max_{|t| \le 1/2}\, (f*f)(t)}%
       {\displaystyle\left(\int f\right)^{\!2}}.
\]
\end{definition}

By homogeneity, we may normalize $\int f = 1$ without loss of
generality, so that $C_{1a} = \inf_{f} \|f*f\|_{L^\infty}$ over
nonnegative $f$ with $\supp(f) \subseteq [-\tfrac14, \tfrac14]$ and
$\int f = 1$.

\medskip

\noindent\textbf{Why this constant matters.}  $C_{1a}$ is connected to
the asymptotic size of Sidon sets in additive combinatorics.  A
\emph{Sidon set} is a set of integers where all pairwise sums are
distinct; equivalently, the ``representation function'' of the sumset
has values at most~2 everywhere except at doubled elements.  The
constant $C_{1a}$ governs how efficiently mass can be distributed to
minimize the peak of the autoconvolution --- the continuous analog of
controlling pairwise-sum collisions.

\subsection{Known Bounds}

\begin{center}
\begin{tabular}{lcl}
  \toprule
  \textbf{Bound} & \textbf{Value} & \textbf{Reference} \\
  \midrule
  Upper bound & $\le 1.5029$ & Matolcsi \& Vinuesa (2010) \\
  Lower bound & $\ge 1.2802$ & Cloninger \& Steinerberger (2017) \\
  \bottomrule
\end{tabular}
\end{center}

The \emph{upper bound} comes from exhibiting explicit functions whose
autoconvolution peak is small.  This is a constructive task: find a
good $f$ and compute its peak.

The \emph{lower bound} is fundamentally harder: one must show that
\emph{no} function can achieve a peak below the threshold.  This
requires exhaustive elimination of all possibilities, which is the
subject of this document.

\subsection{Proof Strategy at a High Level}

The proof proceeds in three conceptual steps:

\begin{enumerate}[label=(\roman*)]
  \item \textbf{Reduce} the infinite-dimensional optimization
    (over all nonnegative functions) to a finite-dimensional one
    (over vectors of bin averages), with a quantified approximation
    error.

  \item \textbf{Discretize} the finite-dimensional simplex to a
    lattice, with a quantified rounding error.

  \item \textbf{Enumerate} every lattice point and verify that each
    one has autoconvolution peak exceeding the target threshold.
    If all are eliminated, the bound is proven.
\end{enumerate}

Step~(iii) is made tractable by pruning strategies (asymmetry,
windowed bounds) and a multiscale cascade (coarse-to-fine refinement).


% ======================================================================
\section{From Functions to Bin Averages}\label{sec:bin}
% ======================================================================

Our first order of business is to replace the infinite-dimensional
optimization --- over all nonnegative functions --- with something
finite-dimensional and computable.

\subsection{The Partition}

Fix a positive integer $n$ (the ``half-bin count'').  Partition
$(-\tfrac14, \tfrac14)$ into $d = 2n$ equal bins:
\[
  I_j \;=\; \left(\frac{j}{4n},\; \frac{j+1}{4n}\right),
  \qquad j = -n, -n+1, \ldots, n-1.
\]
Each bin has width $\tfrac{1}{4n}$.

\begin{remark}
We use $d = 2n$ bins total, indexed from $-n$ to $n-1$.  In the
implementation, we re-index these as $0, 1, \ldots, d-1$ (i.e.,
$j \mapsto j + n$).  The mathematics is the same either way.
\end{remark}

\subsection{Bin Averages}

For any nonnegative $f$ with $\supp(f) \subseteq (-\tfrac14,
\tfrac14)$ and $\int f = 1$, define the \emph{bin averages}:
\[
  a_j \;=\; 4n \int_{I_j} f(x)\, dx \;\ge\; 0,
  \qquad j = 0, \ldots, d-1.
\]

The factor $4n$ normalizes so that each $a_j$ equals the average value
of $f$ on the bin $I_j$ (since $|I_j| = \tfrac{1}{4n}$).  The
constraint $\int f = 1$ becomes
\[
  \sum_{j=0}^{d-1} a_j \;=\; 4n.
\]

\begin{definition}
The \emph{continuous simplex} is
\[
  A_n \;=\; \Bigl\{
    a \in \R_{\ge 0}^d
    \;\Big|\;
    \sum_{j=0}^{d-1} a_j = 4n
  \Bigr\}.
\]
\end{definition}

Every nonnegative function $f$ with $\int f = 1$ maps to a point in $A_n$,
but not every point in $A_n$ arises from a function (the map loses
information about the shape of $f$ within each bin).

\subsection{The Lower Bound on $\|f*f\|_\infty$}

Remarkably, the entire reduction rests on two elementary observations
--- one geometric, one analytic.

\begin{lemma}[Reduction to Bin Averages --- Lemma~1 of CS17]
\label{lem:bin-reduction}
For any $f \in \mathcal{F}$ with $\int f = 1$ and corresponding bin
averages $a = (a_0, \ldots, a_{d-1})$:
\[
  \|f * f\|_{L^\infty}
  \;\ge\;
  \max_{\substack{2 \le \ell \le 2d \\[2pt] k}}
  \frac{1}{4n\ell}
  \sum_{\substack{0 \le i, j \le d-1 \\[1pt] k \le i+j \le k+\ell-2}}
  a_i\, a_j.
\]
\end{lemma}

\begin{proof}[Proof sketch]
\noindent\textbf{Ingredient 1: Support of cross-convolutions.}
Let $f_i = f \cdot \mathbf{1}_{I_i}$ be the restriction of $f$ to bin
$I_i$.  Then $f = \sum_i f_i$ and
\[
  (f * f)(t) \;=\; \sum_{i,j} (f_i * f_j)(t).
\]
The convolution $f_i * f_j$ is supported on the Minkowski sum
$I_i + I_j$, which is an interval of width $\tfrac{1}{2n}$.
The key point: \emph{the index $i + j$ determines which part of the
convolution domain receives the contribution from $f_i * f_j$}.

\medskip
\noindent\textbf{Ingredient 2: Pigeonhole.}
For any nonnegative function $h$ and interval $J$:
$\|h\|_{L^\infty} \ge \tfrac{1}{|J|} \int_J h$.

\medskip
\noindent\textbf{Combining.}  Consider a ``window'' covering
sum-indices $s \in \{k, k+1, \ldots, k + \ell - 2\}$.  The Minkowski
sums for consecutive sum-indices overlap (their centers are spaced
$\tfrac{1}{4n}$ apart, each of width $\tfrac{1}{2n}$), so their
union forms an interval of length exactly $\tfrac{\ell}{4n}$ in the
convolution domain.  All cross-terms $f_i * f_j$ with
$k \le i + j \le k + \ell - 2$ have support within this interval,
contributing total $L^1$ mass
$\sum \tfrac{a_i}{4n} \cdot \tfrac{a_j}{4n}$.  Applying the
pigeonhole bound:
\[
  \|f * f\|_{L^\infty}
  \;\ge\;
  \frac{1}{\ell / (4n)}
  \sum_{\substack{k \le i+j \le k+\ell-2}}
  \frac{a_i\, a_j}{(4n)^2}
  \;=\;
  \frac{1}{4n\ell}
  \sum_{\substack{k \le i+j \le k+\ell-2}}
  a_i\, a_j.
\]
Taking the maximum over all windows gives the result.
\end{proof}

\begin{remark}[Intuition]
Think of the bin averages $a_i$ as describing ``how much mass $f$ puts
in each bin.''  The products $a_i a_j$ measure how much the mass in
bins $i$ and $j$ contribute to the autoconvolution.  The window
argument says: if too much product-mass falls in any fixed interval of
the convolution domain, then $f * f$ must be large somewhere in that
interval.

The reader may wonder: why not just take the narrowest possible window
($\ell = 2$) everywhere?  Because narrow windows see fewer
cross-terms, so their sums can be small even when mass is spread
across many bins.  The interplay between window width and the number of
contributing pairs is what makes the optimization nontrivial.
\end{remark}


% ======================================================================
\section{Discretization of the Simplex}\label{sec:disc}
% ======================================================================

Having reduced the problem to minimizing over the continuous simplex
$A_n$, we face a new obstacle: $A_n$ is uncountable.  To bring the
problem within reach of a computer, we approximate $A_n$ by a finite
lattice, paying a small but quantifiable price in accuracy.

\subsection{The Lattice}

To discretize $A_n$, we need a grid fine enough to approximate any
point in the simplex, yet coarse enough to enumerate.  The natural
choice is a lattice of spacing $1/m$.

\begin{definition}
Fix a positive integer $m$ (the ``grid resolution'').  The
\emph{discrete lattice} is
\[
  B_{n,m} \;=\; \left\{
    b \in \left(\tfrac{1}{m}\N\right)^d
    \;\middle|\;
    \sum_{j=0}^{d-1} b_j = 4n
  \right\},
\]
where each $b_j$ is a nonnegative multiple of $\tfrac{1}{m}$.
\end{definition}

Equivalently, writing $c_j = m \cdot b_j$, the lattice consists of
nonnegative integer vectors $c = (c_0, \ldots, c_{d-1})$ with
$\sum c_j = S$, where $S = 4nm$.  These are the \emph{compositions}
of the integer $S$ into $d$ nonnegative parts.

\begin{remark}[Implementation convention]
The implementation uses a rescaled convention where integer coordinates
sum to $m$ rather than $4nm$, absorbing the factor $4n$ into the
scale when converting to bin averages: $a_j = c_j \cdot 4n / m$.  The
mathematics is equivalent; we use the $S = 4nm$ convention in this
proof for consistency with the bin-average normalization.
\end{remark}

The lattice is useful only if every continuous point has a nearby
lattice point --- otherwise gaps in the lattice could hide the
minimizer.

\begin{lemma}[Lattice as an Approximation --- Lemma~2 of CS17]
\label{lem:lattice-approx}
$B_{n,m}$ is a $\tfrac{1}{m}$-net of $A_n$ in $\ell^\infty$-norm.
That is, for every $a \in A_n$, there exists $b \in B_{n,m}$ with
$\|a - b\|_\infty \le \tfrac{1}{m}$.
\end{lemma}

\begin{proof}[Proof sketch]
Given $a \in A_n$, round each coordinate to the nearest multiple of
$\tfrac{1}{m}$, adjusting to maintain the sum constraint.
Specifically, use a greedy rounding: process coordinates left to
right, maintaining a running deficit $t_i = \sum_{j<i}(b_j - a_j)$.
Round down first, then alternate to keep $-\tfrac{1}{m} < t_{i+1} \le
0$.  The last coordinate is set to enforce the exact sum.  Each
coordinate satisfies $|a_j - b_j| \le \tfrac{1}{m}$.
\end{proof}

\subsection{The Discretization Error Bound}

Since we approximate $a$ by $b$ with per-coordinate error at most
$\tfrac{1}{m}$, the windowed test value changes by a bounded amount.

\begin{lemma}[Discretization Error --- Lemma~3 of CS17]
\label{lem:disc-error}
For any $a \in A_n$ and its nearest lattice point $b \in B_{n,m}$:
\[
  \tv(a) \;\ge\; \tv(b) - \frac{2}{m} - \frac{1}{m^2},
\]
where $\tv(\cdot)$ denotes the maximum windowed test value from
Lemma~\ref{lem:bin-reduction}.  Equivalently,
\[
  C_{1a} \;\ge\; b_{n,m} - \frac{2}{m} - \frac{1}{m^2},
\]
where $b_{n,m} = \min_{b \in B_{n,m}} \tv(b)$.
\end{lemma}

\begin{proof}
Write $a = b + \varepsilon$ where $\|\varepsilon\|_\infty \le
\tfrac{1}{m}$ as vectors of bin averages.  Since $\tv$ is a quadratic
function of its argument (a maximum of quadratic forms), we can bound
the perturbation algebraically.

For any window $(\ell, k)$, the windowed sum
$W_{\ell,k}(a) = \tfrac{1}{4n\ell}\sum_{k \le i+j \le k+\ell-2} a_i a_j$
expands as:
\[
  W_{\ell,k}(b + \varepsilon) = W_{\ell,k}(b)
    + \underbrace{\frac{1}{4n\ell}\sum (b_i \varepsilon_j + \varepsilon_i b_j)}_{\text{cross terms}}
    + \underbrace{\frac{1}{4n\ell}\sum \varepsilon_i \varepsilon_j}_{\text{error-squared}}.
\]

\noindent\textbf{Cross terms.}  For each $j$, the coefficient of
$\varepsilon_j$ is $\tfrac{2}{4n\ell}\sum_{\text{valid }i} b_i \le
\tfrac{2}{4n\ell} \cdot 4n = \tfrac{2}{\ell}$ (since $\sum b_i = 4n$
and each $b_i \ge 0$).  Summing over at most $d$ values of $j$ with
$|\varepsilon_j| \le 1/m$, the total cross-term perturbation per
window is at most $\tfrac{2}{m}$ in absolute value.  (This bound is
conservative; it holds uniformly over all windows.)

\medskip
\noindent\textbf{Error-squared term.}
$\bigl|\tfrac{1}{4n\ell}\sum \varepsilon_i \varepsilon_j\bigr| \le
\tfrac{1}{4n\ell} \cdot (\sum |\varepsilon_i|)^2$.  Since $\sum
|\varepsilon_i| \le d / m = 2n/m$ and $4n\ell \ge 8n$, this is at
most $\tfrac{(2n/m)^2}{8n} = \tfrac{n}{2m^2}$.

\medskip
\noindent Combining: $W_{\ell,k}(a) \ge W_{\ell,k}(b) - 2/m -
n/(2m^2)$ for every window.  Taking the max over windows:
$\tv(a) \ge \tv(b) - 2/m - n/(2m^2)$.

The stated bound $2/m + 1/m^2$ is the weakest case; it holds
because $n/(2m^2) \le 1/m^2$ when $n \le 2$, and the cascade
always begins at $n = 2$ ($d = 4$ bins).  At finer resolutions
($n > 2$), the cascade does not re-invoke the uniform correction
--- it uses the dynamic per-window threshold of
Lemma~\ref{lem:dynamic-correction} instead, which accounts for the
actual contributing mass and does not suffer from this looseness.
Thus the uniform bound $2/m + 1/m^2$ is applied only at the
initial resolution where $n \le 2$, and is tight there.
\end{proof}

\begin{remark}[The correction term in practice]
The correction $\tfrac{2}{m} + \tfrac{1}{m^2}$ is the ``price of
discretization.''  At $m = 20$, it equals $0.1025$; at $m = 50$, it
equals $0.0404$.  Larger $m$ gives a tighter bound but more lattice
points to check --- a tension that drives much of the algorithm design.
\end{remark}

\subsection{The Refined (Dynamic) Correction}

The uniform bound of $2/m$ on the cross-term perturbation is
pessimistic: it assumes every bin contributes to every window.  A
tighter, position-dependent bound exploits the fact that narrow or
edge-positioned windows involve fewer bins.

\begin{lemma}[Dynamic Correction --- Equation~(1) of CS17]
\label{lem:dynamic-correction}
For a specific window at position $k$ with length $\ell$, let
$W_{\text{int}} = \sum_{i \in \mathcal{B}(k,\ell)} c_i$ be the total
integer mass in contributing bins, where $\mathcal{B}(k,\ell) = \{i :
\exists\, j \text{ with } k \le i+j \le k+\ell-2\}$.  Then the
\emph{window-specific effective threshold} is:
\[
  T_{\ell,k} \;=\; c_{\mathrm{target}}
    + \frac{1 + 2\, W_{\mathrm{int}}}{m^2}
\]
rather than the uniform
$T = c_{\mathrm{target}} + \tfrac{2}{m} + \tfrac{1}{m^2}$.
\end{lemma}

\begin{proof}
For the window at $(\ell, k)$, the cross-term perturbation is bounded
by $\tfrac{2}{4n\ell} \cdot \tfrac{1}{m} \sum_{i \in \mathcal{B}}
b_i = \tfrac{2W}{4n\ell m}$ where $W = W_{\text{int}}/m$.  In integer
coordinates (multiplying the test-value inequality through by
$4n\ell\, m^2$), the windowed sum $\sum c_i c_j$ is compared against:
\[
  \text{int\_thresh}
  \;=\;
  \bigl\lfloor
    \bigl(c_{\mathrm{target}} \cdot m^2 + 1
      + 2\,W_{\text{int}}\bigr)
    \cdot \frac{\ell}{4n}
    \cdot (1 - 4\epsilon_{\mathrm{mach}})
  \bigr\rfloor,
\]
where the $(1 - 4\epsilon_{\mathrm{mach}})$ factor guards against
floating-point rounding, and the $+1$ term provides an additional
safety margin.  Both make the threshold conservative (the code may fail
to prune a borderline case, but it will never falsely prune).
\end{proof}

\begin{remark}[Why dynamic is better]
The uniform correction uses $W_{\text{int}} = S = 4nm$ (the total
mass).  The dynamic correction uses the actual mass in contributing
bins, which can be much smaller for narrow windows near the edges of
the convolution domain.  This makes the effective threshold lower
(easier to exceed), allowing more configurations to be pruned.
\end{remark}

% ======================================================================
\section{The Windowed Test Value}\label{sec:testvalue}
% ======================================================================

With the discretization machinery in hand, we can describe precisely
what the algorithm computes at each lattice point.

\subsection{Definition}

\begin{definition}
For a mass vector $a = (a_0, \ldots, a_{d-1})$ with $a_i \ge 0$ and
$\sum a_i = 4n$, the \emph{autoconvolution} is the vector of length
$2d - 1$:
\[
  \conv[s] \;=\; \sum_{\substack{i + j = s \\[1pt] 0 \le i,j \le d-1}}
  a_i\, a_j,
  \qquad s = 0, 1, \ldots, 2(d-1).
\]
The \emph{test value} is
\[
  \tv(a) \;=\;
  \max_{\substack{2 \le \ell \le 2d \\[2pt] 0 \le k \le 2(d-1) - (\ell-2)}}
  \frac{1}{4n\ell}
  \sum_{s=k}^{k+\ell-2} \conv[s].
\]
\end{definition}

In words: compute the autoconvolution, slide a window of each possible
width $\ell$ across it, sum the $\ell - 1$ consecutive entries in each
window position, normalize by $4n\ell$, and take the maximum.

\subsection{Efficient Computation via Prefix Sums}

The test value can be computed efficiently using prefix sums.  Let
$P[s] = \sum_{k=0}^{s} \conv[k]$ be the prefix sum of the
autoconvolution.  Then the windowed sum from $s_{\text{lo}}$ to
$s_{\text{hi}}$ is:
\[
  \sum_{s=s_\text{lo}}^{s_\text{hi}} \conv[s]
  \;=\;
  P[s_\text{hi}] - P[s_\text{lo} - 1]
  \qquad (\text{with } P[-1] = 0).
\]

\begin{remark}[Complexity]
Computing the autoconvolution takes $O(d^2)$ time (or $O(d \log d)$
via FFT, though the direct method is faster for the small $d$ values
used here).  The prefix sum takes $O(d)$.  Evaluating all windows
takes $O(d^2)$ time (summing over $O(d)$ window widths and $O(d)$
positions each).  Total: $O(d^2)$ per lattice point.
\end{remark}

\subsection{Reversal Symmetry}\label{subsec:reversal}

A key structural observation cuts the search space in half.  If we
reverse the order of the bins, the autoconvolution peak does not change
--- intuitively, because convolution does not care which direction we
label the support.

\begin{theorem}[Autoconvolution Reversal Symmetry]
\label{thm:reversal}
For any mass vector $a$, $\tv(a) = \tv(\rev(a))$, where
$\rev(a) = (a_{d-1}, \ldots, a_0)$.
\end{theorem}

\begin{proof}
The argument has three moving parts.

\medskip
\noindent\textbf{Step 1: Autoconvolution reversal.}
Let $a' = \rev(a)$, so $a'_i = a_{d-1-i}$.  Then:
\[
  \conv'[s]
  \;=\; \sum_{i+j=s} a'_i a'_j
  \;=\; \sum_{i+j=s} a_{d-1-i}\, a_{d-1-j}.
\]
Substituting $i' = d-1-i$, $j' = d-1-j$ (so $i'+j' = 2(d-1) - s$):
\[
  \conv'[s] \;=\; \conv[2(d-1) - s].
\]
That is, the autoconvolution of the reversal is the reversal of the
autoconvolution.

\medskip
\noindent\textbf{Step 2: Window-sum bijection.}
A window sum of width $w = \ell - 1$ starting at $s_0$ transforms
under reversal to a window sum of the same width starting at
$2(d-1) - s_0 - w + 1$:
\begin{align*}
  \sum_{s=s_0}^{s_0+w-1} \conv'[s]
  &= \sum_{s=s_0}^{s_0+w-1} \conv[2(d-1)-s] \\
  &= \sum_{s'=2(d-1)-s_0-w+1}^{2(d-1)-s_0} \conv[s'].
\end{align*}
This is a window of the same width $w$, so the multiset of all window
sums at width $w$ is identical for $\conv$ and $\conv'$.

\medskip
\noindent\textbf{Step 3: Normalization preserves the maximum.}
The normalization $\tfrac{1}{4n\ell}$ depends only on $\ell$, not the
window position.  Since the multiset of window sums is identical at
each width, $\tv(a) = \tv(a')$.
\end{proof}

\begin{corollary}[Canonical Symmetry]
It suffices to check only \emph{canonical} compositions $b$ satisfying
$b \le \rev(b)$ lexicographically.  This halves the search space (up
to palindromes).
\end{corollary}

Even after exploiting reversal symmetry, the number of lattice points
to check --- roughly $\binom{S+d-1}{d-1}/2$ --- grows rapidly with $d$
and $m$.  To keep the computation tractable, we need ways to rule out
large swathes of the simplex without computing the full test value.


% ======================================================================
\section{Pruning Strategies}\label{sec:pruning}
% ======================================================================

\subsection{Asymmetry Pruning}

At first glance, the following bound might seem too crude to be useful:
it ignores everything about $f$ except how much mass sits on each half
of the support.  Yet in practice, this single test eliminates the vast
majority of configurations at every cascade level.

\begin{theorem}[Asymmetry Bound]
\label{thm:asymmetry}
Let $f \ge 0$ with $\supp(f) \subseteq (-\tfrac14, \tfrac14)$ and
$\int f = 1$.  Let $L = \int_{-1/4}^{0} f$ be the left-half mass.
Then:
\[
  \|f * f\|_{L^\infty} \;\ge\; 2L^2.
\]
\end{theorem}

\begin{proof}
Consider the left-left convolution:
\[
  (f * f)(t) \;=\; \int f(x)\, f(t-x)\, dx
  \;\ge\; \int_{-1/4}^{0} f(x)\, f(t-x)\, \mathbf{1}_{[-1/4,0]}(t-x)\, dx
\]
for $t \in (-\tfrac12, 0)$.  By Fubini's theorem, the total mass of
$f * f$ restricted to $(-\tfrac12, 0)$ is at least $L^2$ (the
left-left contribution).  Since $|(-\tfrac12, 0)| = \tfrac12$:
\[
  \|f * f\|_{L^\infty} \;\ge\; \frac{L^2}{1/2} \;=\; 2L^2.
\]
By symmetry, the same holds for the right-half mass $R = 1 - L$:
$\|f*f\|_\infty \ge 2R^2$.  Therefore
$\|f*f\|_\infty \ge 2 \max(L^2, R^2)$.
\end{proof}

\begin{corollary}[Asymmetry Threshold]
\label{cor:asym-threshold}
If $2L^2 \ge c_{\mathrm{target}}$, i.e.,
$L \ge \sqrt{c_{\mathrm{target}}/2}$, then the configuration is
ruled out.  The threshold left-mass fraction is:
\[
  p^* \;=\; \sqrt{c_{\mathrm{target}} / 2}.
\]
For $c_{\mathrm{target}} = 1.4$: $p^* \approx 0.8367$.
\end{corollary}

\begin{remark}[No discrete margin needed]
One might expect a safety margin to account for the discrepancy between
discrete and continuous left-mass fractions.  However, our discrete
compositions represent piecewise-constant step functions, for which the
left-half mass $L = \sum_{i < n} c_i / S$ is \emph{exact} --- no
approximation is involved.  Moreover, the midpoint $x = 0$ always
falls on a bin boundary, and the left-mass fraction is preserved
exactly under dyadic refinement (child bins for the left half sum to
the parent's left bins).  Therefore no margin is necessary: we prune
at the exact threshold $p^*$.
\end{remark}

\begin{remark}[Important subtlety]
The asymmetry bound is a \emph{direct} $L^\infty$ bound on $f * f$.
It does \emph{not} go through the discretization framework of
Lemma~\ref{lem:disc-error}, so we compare against
$c_{\mathrm{target}}$ itself (not $c_{\mathrm{target}} + \tfrac{2}{m}
+ \tfrac{1}{m^2}$).
\end{remark}

\subsection{Contiguous Block-Sum Bound}

\begin{theorem}[Block-Sum Bound]
\label{thm:block-sum}
For any contiguous block of $p$ bins $\{q, q+1, \ldots, q+p-1\}$
with block sum $B = \sum_{i=q}^{q+p-1} c_i$ (in integer coordinates):
\[
  \tv(a) \;\ge\; \frac{B^2}{4n \cdot 2p \cdot m^2}.
\]
\end{theorem}

\begin{proof}
Consider the window of length $\ell = 2p$ starting at $k = 2q$ (in
sum-index space).  This window captures $\ell - 1 = 2p - 1$
consecutive autoconvolution values at indices $2q, 2q+1, \ldots,
2(q+p-1)$.

All \emph{intra-block} pairs $(i,j)$ with $q \le i,j \le q+p-1$
satisfy $2q \le i+j \le 2(q+p-1)$, so they fall within this window.
Their contribution is:
\[
  \sum_{\substack{q \le i \le q+p-1 \\ q \le j \le q+p-1}} a_i a_j
  \;=\; \left(\sum_{i=q}^{q+p-1} a_i\right)^{\!2}
  \;=\; \frac{B^2}{m^2}.
\]
Since all $a_i \ge 0$, the cross-block pairs contribute $\ge 0$, so
the full window sum is at least $B^2/m^2$.  Normalizing:
\[
  \tv(a) \;\ge\; \frac{B^2/m^2}{4n \cdot 2p}
  \;=\; \frac{B^2}{4n \cdot 2p \cdot m^2}. \qedhere
\]
\end{proof}

\begin{remark}[Special cases]
\leavevmode
\begin{itemize}
  \item $p = 1$ (single bin): bound $= c_i^2 / (8n m^2)$.  This is
    the ``max-element'' check.
  \item $p = n$ (half the bins): bound $=
    (\text{left sum})^2 / (4n \cdot d \cdot m^2)$.  This connects to
    the asymmetry argument.
  \item Intermediate $p$ values catch configurations where mass is
    concentrated in a middle block, evading both the max-element and
    asymmetry checks.
\end{itemize}
\end{remark}

\subsection{Two-Max Cross-Term Bound}

When mass is spread between two bins rather than concentrated in one,
a cross-term argument gives a stronger bound than the single-element
check.

\begin{theorem}[Two-Max Bound]
\label{thm:two-max}
Let $c_{p_1}$ and $c_{p_2}$ be the two largest values in $c$, with
$p_1 \ne p_2$.  Then:
\[
  \tv(a) \;\ge\; \frac{2\, c_{p_1}\, c_{p_2}}{8n\, m^2}.
\]
\end{theorem}

\begin{proof}
The autoconvolution at index $s = p_1 + p_2$ satisfies:
\[
  \conv[p_1 + p_2]
  \;=\; \sum_{i+j = p_1+p_2} a_i a_j
  \;\ge\; a_{p_1} a_{p_2} + a_{p_2} a_{p_1}
  \;=\; 2\, a_{p_1}\, a_{p_2}
  \;=\; \frac{2\, c_{p_1}\, c_{p_2}}{m^2}.
\]
This single entry is an $\ell = 2$ window:
\[
  \tv(a) \;\ge\; \frac{\conv[p_1+p_2]}{4n \cdot 2}
  \;\ge\; \frac{2\, c_{p_1}\, c_{p_2}}{8n\, m^2}. \qedhere
\]
\end{proof}

\begin{remark}
This dominates the single-element bound $c_{p_1}^2 / (8nm^2)$ whenever
$2 c_{p_2} > c_{p_1}$, i.e., when mass is spread between the top two
elements rather than concentrated in one.
\end{remark}

\subsection{Canonical Symmetry Exploitation}

By Theorem~\ref{thm:reversal}, $\tv(b) = \tv(\rev(b))$ for every
lattice point $b$.  This motivates the following notion of canonicality.

\begin{definition}
A composition $b$ is \emph{canonical} if $b \le \rev(b)$
lexicographically.  That is, comparing $b_0$ with $b_{d-1}$, then
$b_1$ with $b_{d-2}$, etc., $b$ comes first (or they are equal, i.e.,
$b$ is a palindrome).
\end{definition}

\begin{proposition}[Canonical Count]
\label{prop:canon-count}
The number of canonical compositions is $\tfrac{N + P}{2}$, where
$N = \binom{S+d-1}{d-1}$ is the total count and $P$ is the number of
palindromes.
\end{proposition}

\begin{proof}
Every composition falls into exactly one of three categories:
palindromes (those equal to their own reversal), strictly canonical
non-palindromes ($b < \rev(b)$), and their reversals.  Since reversal
is an involution with no fixed points outside the palindromes, the
second and third categories have equal size $C$.  Counting gives
$N = P + 2C$, so the canonical count is $P + C = (N+P)/2$.
\end{proof}

\begin{remark}[Loop-bound tightening for $d = 4$]
For $b = (c_0, c_1, c_2, c_3)$ with $c_3 = S - c_0 - c_1 - c_2$,
canonicality ($b \le \rev(b)$) requires $c_0 \le c_3$, giving three
loop bounds:
\begin{itemize}
  \item $c_0 \le \lfloor S/2 \rfloor$ \quad (if $c_0 > S/2$ then
    $c_3 < c_0$).
  \item $c_1 \le S - 2c_0$ \quad (need $c_2 \ge 0$ with
    $c_1 + c_2 \le S - 2c_0$).
  \item $c_2 \le S - 2c_0 - c_1$ \quad (ensures $c_3 \ge c_0$).
\end{itemize}
Plus a palindrome filter: when $c_0 = c_3$, require $c_1 \le c_2$.

For $d = 6$, analogous bounds apply: $c_0 \le \lfloor S/2 \rfloor$,
$c_4 \le S - c_0 - c_1 - c_2 - c_3 - c_0$, with equality checks for
the inner pairs when outer pairs tie.
\end{remark}


% ======================================================================
\section{The Multiscale Cascade}\label{sec:cascade}
% ======================================================================

Brute-force enumeration at fine resolution is hopelessly infeasible ---
even modest parameters yield billions of lattice points.  The key idea,
borrowed from multigrid methods in numerical analysis, is to start
coarse: most configurations can be ruled out cheaply at low resolution,
and only the stubborn survivors need to be examined more closely.

\subsection{Overview}

\begin{enumerate}[label=\textbf{Step \arabic*:}]
  \item \textbf{Start coarse.}  At level $L_0$, enumerate all
    canonical compositions in $B_{n_0, m}$ with $d_0 = 2n_0$ bins
    (e.g., $n_0 = 2$, $d_0 = 4$).

  \item \textbf{Prune.}  For each composition, apply asymmetry
    pruning and compute the windowed test value.  If the test value
    exceeds the effective threshold $T$, the composition is eliminated.

  \item \textbf{Refine survivors.}  Each surviving composition at
    resolution $d$ is refined to resolution $2d$ by \emph{dyadic
    splitting}: each bin is split into two sub-bins.

  \item \textbf{Repeat.}  Prune the refined compositions.  Continue
    until either all are eliminated (proof complete) or a
    computational budget is reached.
\end{enumerate}

\subsection{Dyadic Splitting (Refinement)}

Given a parent composition $b = (b_0, \ldots, b_{d-1})$ at resolution
$d$, the refinement produces children $c = (c_0, c_1, \ldots,
c_{2d-1})$ at resolution $2d$, where:
\[
  c_{2i} + c_{2i+1} \;=\; b_i \qquad \text{for each } i = 0, \ldots, d-1,
\]
with $c_{2i}, c_{2i+1} \ge 0$ and both being nonnegative integers.

\subsection{Energy Cap}\label{subsec:energy-cap}

One might worry that generating all possible children is wasteful.
Indeed, many children are immediately ruled out by the single-bin
diagonal window.  The energy cap avoids generating them in the first
place.

Recall that $a_j = c_j / m$ and the $\ell = 2$ diagonal window at
position $2j$ gives $\tv(a) \ge a_j^2 / (8n_{\text{child}}) =
c_j^2 / (8 n_{\text{child}} m^2)$.  We cap each child bin at:
\[
  x_{\text{cap}} \;=\;
  \left\lfloor m \cdot \sqrt{8 n_{\text{child}} \cdot T} \right\rfloor,
\]
where $T = c_{\mathrm{target}} + \tfrac{2}{m} + \tfrac{1}{m^2}$.

\begin{proposition}[Energy Cap Soundness]
If $c_j > x_{\mathrm{cap}}$, then $\tv(a) > T$.
\end{proposition}

\begin{proof}
The $\ell = 2$ window at position $2j$ gives:
\[
  \tv(a) \;\ge\; \frac{\conv[2j]}{8 n_{\text{child}}}
  \;\ge\; \frac{c_j^2}{8 n_{\text{child}}\, m^2}.
\]
With $c_j > m \sqrt{8 n_{\text{child}} T}$:
\[
  \frac{c_j^2}{8 n_{\text{child}}\, m^2}
  \;>\; \frac{m^2 \cdot 8 n_{\text{child}} \cdot T}
             {8 n_{\text{child}}\, m^2}
  \;=\; T. \qedhere
\]
\end{proof}

\begin{remark}[Tighter Cauchy--Schwarz cap]
The implementation also applies a second, tighter cap based on a direct
Cauchy--Schwarz bound on $\|f*f\|_\infty$ that does not go through the
test-value discretization (analogous to how asymmetry pruning bypasses
the correction term).  This gives $x_{\text{cap,CS}} = \lfloor m
\sqrt{8 n_{\text{child}} \cdot c_{\text{target}}} \rfloor \le
x_{\text{cap}}$, and the implementation uses $\min(x_{\text{cap}},
x_{\text{cap,CS}})$.  Both caps are sound; the tighter one simply
prunes more aggressively.
\end{remark}

\subsection{Cascade Soundness}

\begin{theorem}[Cascade Soundness]
\label{thm:cascade-sound}
If the cascade terminates with zero survivors at some level $L_k$
(with resolution $d_k = d_0 \cdot 2^k$), then
$C_{1a} \ge c_{\mathrm{target}}$.
\end{theorem}

\begin{proof}
We argue by induction on the cascade level.  At level $L_0$,
completeness is straightforward: every canonical composition is
enumerated, and reversal symmetry (Theorem~\ref{thm:reversal})
accounts for the rest.

For the inductive step, suppose every composition at level $k$ is
either directly pruned or refined.  A refined composition's children
are all generated and tested at level $k+1$; if every child is pruned,
the parent is indirectly eliminated, since any continuous function
close to the parent at resolution $d_k$ must be close to one of its
children at resolution $d_{k+1}$.  (This follows because the level-$k$
bin averages are determined by summing adjacent pairs of level-$(k+1)$
bin averages, so the parent-child relationship is surjective onto the
full level-$(k+1)$ lattice.)

When the cascade reaches a level with zero survivors, the net property
of the lattice (Lemma~\ref{lem:lattice-approx}) ensures that every
continuous vector $a$ has a nearby lattice point with test value at
least $T$, and the discretization error bound
(Lemma~\ref{lem:disc-error}) finishes the job:
\[
  \|f*f\|_\infty \ge \tv(a) \ge \tv(b) - \frac{2}{m} - \frac{1}{m^2}
  \ge T - \frac{2}{m} - \frac{1}{m^2} = c_{\mathrm{target}}.
\]
Since $f$ was arbitrary, $C_{1a} \ge c_{\mathrm{target}}$.
\end{proof}

\subsection{Canonical Handling Across Levels}

At level $L_0$, only canonical compositions are generated.  At levels
$L_1$ and beyond, the situation is more subtle:

\begin{itemize}
  \item Children of a canonical parent $P$ are \emph{not} necessarily
    canonical.
  \item The reversal $\rev(P)$ is \emph{not} in the parent list
    (unless $P$ is a palindrome), so its children are not generated
    directly.
  \item However, if $C$ is a child of $P$, then $\rev(C)$ is a child
    of $\rev(P)$.  Since $\tv(C) = \tv(\rev(C))$
    (Theorem~\ref{thm:reversal}), testing $C$ suffices for both.
\end{itemize}

Therefore at levels $\ge 1$:
\begin{enumerate}
  \item Generate \emph{all} children of each parent (no canonical
    filter during generation).
  \item Test each child against the threshold.
  \item \emph{Canonicalize} survivors: replace each with
    $\min(C, \rev(C))$ lexicographically.
  \item \emph{Deduplicate}: remove duplicate canonical forms (children
    from different parents, or a palindrome parent producing both $C$
    and $\rev(C)$).
\end{enumerate}

\begin{proposition}[Completeness of Canonical Handling]
This procedure tests every composition at the child resolution:
if $C'$ is any child-level composition and $P' = \text{parent}(C')$,
then either $P'$ or $\rev(P')$ is in the parent list, and $C'$ or
$\rev(C')$ is among the tested children.
\end{proposition}

\subsection{Fused Generate-and-Prune Kernel}

At deep cascade levels, each parent may have millions of children.
The fused kernel generates and tests each child inline via a
Cartesian-product odometer, never materializing the full children
array:

\begin{itemize}
  \item \textbf{Incremental autoconvolution:} when only the last
    cursor position changes ($\sim$67\% of steps), the raw
    autoconvolution is updated in $O(d)$ instead of $O(d^2)$.
  \item \textbf{Quick-check:} re-tries the previous killing window
    before a full scan.
  \item \textbf{Subtree pruning:} on deep carries, checks the
    partial autoconvolution of fixed bins against worst-case unfixed
    mass; if it exceeds the threshold, the entire subtree is skipped.
\end{itemize}


% ======================================================================
\section{The Complete Proof}\label{sec:algorithm}
% ======================================================================

\subsection{Algorithm}

\begin{algorithm}[H]
\caption{Prove $C_{1a} \ge c_{\text{target}}$}
\label{alg:cascade}
\begin{algorithmic}[1]
\Require $c_{\text{target}}$, grid resolution $m$, starting half-bins
  $n_0$, max levels $L_{\max}$
\State $T \gets c_{\text{target}} + 2/m + 1/m^2$
  \Comment{Effective threshold}
\State $d_0 \gets 2 n_0$
\State Generate all canonical compositions of $S = 4 n_0 m$ into
  $d_0$ parts
\State Apply asymmetry pruning (threshold
  $\sqrt{c_{\text{target}}/2}$)
\State Compute test values for remaining compositions; prune those
  with $\tv \ge T$
\State $\text{survivors}_0 \gets$ unpruned compositions
\For{$k = 1, 2, \ldots, L_{\max}$}
  \State $d_k \gets 2 d_{k-1}$; \quad
    $n_k \gets 2 n_{k-1}$
  \State $x_{\text{cap}} \gets \lfloor m \sqrt{8 n_k \cdot T} \rfloor$
  \ForAll{parent $P \in \text{survivors}_{k-1}$}
    \ForAll{children $C$ of $P$ (dyadic split with energy cap)}
      \State Apply asymmetry pruning to $C$
      \If{not asymmetry-pruned}
        \State Compute $\tv(C)$ via windowed autoconvolution
        \If{$\tv(C) \ge T$ (using dynamic per-window threshold)}
          \State Prune $C$
        \Else
          \State $C$ survives; canonicalize and store
        \EndIf
      \EndIf
    \EndFor
  \EndFor
  \State Deduplicate survivors (canonicalize $\to$ sort $\to$ scan)
  \State $\text{survivors}_k \gets$ deduplicated survivors
  \If{$|\text{survivors}_k| = 0$}
    \State \Return \textsc{Proven}: $C_{1a} \ge c_{\text{target}}$
  \EndIf
\EndFor
\State \Return \textsc{Inconclusive}:
  $|\text{survivors}_{L_{\max}}|$ compositions remain
\end{algorithmic}
\end{algorithm}

\subsection{Main Theorem}

\begin{theorem}[Main Result]
\label{thm:main}
If Algorithm~\ref{alg:cascade} returns \textsc{Proven} with
parameters $(c_{\mathrm{target}}, m, n_0)$, then
$C_{1a} \ge c_{\mathrm{target}}$.
\end{theorem}

\begin{proof}
Fix any $f \in \mathcal{F}$ with $\int f = 1$, and let $a$ denote its
bin averages at resolution $d_k$.  Lemma~\ref{lem:bin-reduction} gives
$\|f*f\|_\infty \ge \tv(a)$.  Since $B_{n_k, m}$ is a $1/m$-net of
$A_{n_k}$, there is a lattice point $b$ with $\|a - b\|_\infty \le
1/m$, and the discretization bound (Lemma~\ref{lem:disc-error}) yields
$\tv(a) \ge \tv(b) - 2/m - 1/m^2$.  But the cascade has pruned every
lattice point, so $\tv(b) \ge T$.  Chaining these inequalities:
\[
  \|f*f\|_\infty
  \;\ge\; \tv(a)
  \;\ge\; \tv(b) - \frac{2}{m} - \frac{1}{m^2}
  \;\ge\; T - \frac{2}{m} - \frac{1}{m^2}
  \;=\; c_{\mathrm{target}}.
\]
Since $f$ was arbitrary, $C_{1a} \ge c_{\mathrm{target}}$.
\end{proof}


% ======================================================================
\section{Correctness Invariants}\label{sec:correctness}
% ======================================================================

Stating the algorithm is only half the battle.  For the proof to carry
mathematical weight, we must verify that the implementation faithfully
realizes the specification.  Four invariants pin down exactly what
``faithful'' means.

\subsection{Invariant 1: Complete Enumeration}

Every composition $b \in B_{n,m}$ must be either directly checked or
shown to be covered by a checked ancestor and all its refinements.

\begin{itemize}
  \item At $L_0$: all $\binom{S + d_0 - 1}{d_0 - 1}$ compositions
    are enumerated (in canonical form, with reversal symmetry).
    Verified by comparing the generator output count against the
    stars-and-bars formula, and by checking completeness, uniqueness,
    non-negativity, and sum constraints.
  \item At $L_k$ ($k \ge 1$): all children of all surviving parents
    are generated (no sampling or probabilistic skipping).
\end{itemize}

\subsection{Invariant 2: All Windows Checked}

For each composition that is not eliminated by asymmetry, every valid
window $(\ell, k)$ with $2 \le \ell \le 2d$ and all valid starting
positions $k$ must be tested before the composition is declared a
survivor.  Early exit occurs only \emph{after} a pruning window is
found --- never for survivors.

\subsection{Invariant 3: Conservative Arithmetic}

Floating-point arithmetic is the Achilles' heel of computer-assisted
proofs: a single rounding error in the wrong direction could cause a
valid configuration to be falsely pruned, invalidating the entire
argument.  We guard against this as follows:

\begin{itemize}
  \item Integer coordinates: the autoconvolution is computed in
    integer arithmetic ($c_i c_j$ are exact integers), avoiding
    round-off entirely.
  \item Conservative threshold: the integer threshold includes a
    $(1 - 4\epsilon_{\text{mach}})$ safety factor, making it
    \emph{lower} than the true mathematical threshold.  This means
    the check $\text{ws} > \text{int\_thresh}$ is a \emph{sufficient}
    condition for pruning, never a false positive.
  \item The additional $+1 + 10^{-9} m^2$ term in the code's base
    threshold further ensures conservatism (this term is omitted from
    the mathematical formulas for clarity, but makes the code strictly
    more conservative than what the formulas describe).
\end{itemize}

\subsection{Invariant 4: Refinement Completeness}

Every refinement of a surviving parent must be checked at the finer
level.  The dyadic splitting with energy cap generates all valid
children (Section~\ref{subsec:energy-cap}), and children exceeding the
energy cap are provably pruned.


% ======================================================================
\section{Computational Verification}\label{sec:verification}
% ======================================================================

The correctness of the implementation has been verified through
multiple independent checks.

\subsection{Composition Generators}

\begin{itemize}
  \item \textbf{Completeness}: For 7 parameter combinations $(d, S)$,
    the generator output count matches $\binom{S+d-1}{d-1}$ exactly.
    All outputs sum to $S$, are non-negative, and are unique.
  \item \textbf{Specialized $\equiv$ generic}: The $d=4$ and $d=6$
    specialized generators produce identical sets to the generic
    stack-based generator.
  \item \textbf{Canonical correctness}: For 8 parameter combinations,
    canonical generators produce exactly $\tfrac{N+P}{2}$ outputs, all
    satisfying $b \le \rev(b)$, with every non-canonical $b$ having
    $\rev(b)$ in the output.
  \item \textbf{Batch boundaries}: Across 9 configurations and 8
    batch sizes, output is identical regardless of where batch
    boundaries fall (160 checks, all pass).
\end{itemize}

\subsection{Test Value Computation}

\begin{itemize}
  \item Reversal symmetry ($\tv(b) = \tv(\rev(b))$) verified
    exhaustively for $d=4, S=8$ (165 compositions) and $d=6, S=6$
    (462 compositions), plus 1,500 random tests.  Zero mismatches.
  \item Pure-Python reference implementation agrees with Numba JIT
    kernel on all 891 canonical compositions at $d=4, m=20$.
\end{itemize}

\subsection{Pruning Correctness}

\begin{itemize}
  \item No over-pruning: zero compositions pruned whose true test
    value is below the dynamic threshold.
  \item No missed prunes: zero compositions not pruned whose true
    test value exceeds the dynamic threshold.
  \item Asymmetry filter verified to be exactly symmetric under
    reversal.
\end{itemize}

\subsection{MATLAB Baseline Comparison}

The cascade prover's dynamic threshold formula has been verified
algebraically equivalent to the original MATLAB code of
Cloninger--Steinerberger, with the Python implementation being
strictly more conservative (harder to prune) due to safety margins.


% ======================================================================
\section{Discussion}\label{sec:discussion}
% ======================================================================

\subsection{Relationship to the Original CS17 Proof}

Our framework is a direct extension of Cloninger \& Steinerberger
(2017).  The key differences:

\begin{enumerate}
  \item \textbf{Dynamic correction}: We use the per-window
    position-dependent correction (Lemma~\ref{lem:dynamic-correction})
    instead of the uniform $\tfrac{2}{m} + \tfrac{1}{m^2}$.  This
    prunes more aggressively while remaining mathematically rigorous.

  \item \textbf{Multiscale cascade}: CS17 used $m = 50$ and refined
    from $n = 3$ through $n = 24$.  We use $m = 20$ with dyadic
    refinement from $d = 4$ through $d = 64$, exploiting the fused
    kernel's efficiency.

  \item \textbf{Fused generation}: Instead of materializing all
    children and then testing, we generate and test each child inline,
    reducing memory from $O(N_{\text{children}} \cdot d)$ to $O(d)$
    per parent.

  \item \textbf{Integer arithmetic}: Autoconvolution and threshold
    comparisons use exact integer operations, with floating-point
    involved only in the conservative threshold computation.
\end{enumerate}

\subsection{Limitations}

\begin{itemize}
  \item The proof is \emph{computer-assisted}: the mathematical
    argument reduces correctness to a finite computation, but that
    computation must be performed by a machine.  The invariants in
    Section~\ref{sec:correctness} ensure that the computation is
    trustworthy.

  \item The approach is limited by the exponential growth of the
    composition count with $d$ and $m$.  The multiscale cascade
    mitigates this, but very aggressive targets
    ($c_{\mathrm{target}}$ close to $C_{1a}$) will require more
    cascade levels and higher computational cost.
\end{itemize}


% ======================================================================
\section*{Acknowledgments}
% ======================================================================

This work builds on the foundational algorithm of Cloninger and
Steinerberger~\cite{CS17}.  The constant $C_{1a}$ is tracked in
Tao~et~al.'s optimization constants repository~\cite{Tao}.


% ======================================================================
% References
% ======================================================================

\begin{thebibliography}{9}

\bibitem{CS17}
A.~Cloninger and S.~Steinerberger,
\emph{On Suprema of Autoconvolutions with an Application to Sidon Sets},
Proc.\ AMS \textbf{145}(8), 3191--3200, 2017.
\href{https://arxiv.org/abs/1403.7988}{arXiv:1403.7988}.

\bibitem{MV10}
M.~Matolcsi and C.~Vinuesa,
\emph{Improved bounds on the supremum of autoconvolutions},
J.\ Math.\ Anal.\ Appl.\ \textbf{372}(2), 439--447, 2010.
\href{https://arxiv.org/abs/0907.1379}{arXiv:0907.1379}.

\bibitem{White22}
E.~White,
\emph{New upper bounds on the supremum of autoconvolutions}, 2022.
\href{https://arxiv.org/abs/2210.16437}{arXiv:2210.16437}.

\bibitem{BL25}
E.~Boyer and Z.~Li,
\emph{Improved lower bounds on autoconvolution suprema}, 2025.
\href{https://arxiv.org/abs/2506.16750}{arXiv:2506.16750}.

\bibitem{Tao}
T.~Tao et al.,
\emph{Optimization Problems Repository},
\url{https://teorth.github.io/optimizationproblems/constants/1a.html}.

\end{thebibliography}

\end{document}
